---
title: "L7. Regression models(week4)"
output:
  pdf_document: default
  html_document: default
---

#### Name : Taesoon Kim
#### Date : Jul-05-2017

## Executive summary
Cars can be evaluated by mpg(miles per gallon). If mpg is higher, it is possible to operate more efficiently with less money. I will check which variables are going to affect mpg values using linear regression model.
First, using simple linear regression model, I compare mpg level according to transmission ways. I use lm() function in R, and check the relationship between variables, mpg and transmission methods. In conclusion, they have a close relationship, and there is a difference 7.24 mpg whether using automatic transmission and manual transmission.
Second, I want to confirm which variables are affected to mpg levels besides the transmission method. As I exclude the variable sequentially, I check the adjusted R squared value. As a result, when I use various variables, I can make more sophisticated results.

## Analysis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Load data and check MPG column

```{r load}
# Load dataset
data(mtcars)

#check the "mtcars" data
str(mtcars)

# Change from num to factor
mtcars$am[mtcars$am==1]<-"Manual"
mtcars$am[mtcars$am==0]<-"Automatic"
mtcars$am<-as.factor(mtcars$am)
```

There are 32 rows and 11 columns in "mtcars" data set. Of the 11 variables, mpg means miles per gallon, and am means an automatic and manual transmission. Mpg consists of numbers which mean how many miles can go in one gallon. Am consists of 2 numbers, 0 and 1. 0 means automatic transmission, 1 means manual transmission.
I changed the am variable as a factor.

### Exploratory data analysis

```{r MPG}
# Focus on MPG and draw a histogram
summary(mtcars$mpg)  # mpg consists of numbers

# Draw a histogram and check the relationship between mpg & transmission
par(mfrow=c(1,2))

hist(mtcars$mpg,breaks=10,main="Freq. of Miles per Gallon",xlab="MPG")
boxplot(mpg~am,mtcars,main="MPG by Transmission",xlab="Transmission",ylab="MPG")
```

The largest number of MPG data is located in the 14~16 range. And also I can check that manual transmission uses more gas than automatic transmission.

### Hypothesis testing(Statistical Inference)

```{r t-test}
# Define new variable and store new data frame
mtcars_auto<-mtcars[mtcars$am=="Automatic",]
mtcars_manu<-mtcars[mtcars$am=="Manual",]

t.test(mtcars_auto$mpg,mtcars_manu$mpg)
```

P-value is less than 0.05, so it indicates strong evidence against the null hypothesis. 
The mean difference between automatic and manual is 7.24494.

### Simple linear regression

```{r regression}
# Using "lm()" function, consider linear regression
fit_mtcars<-lm(mpg~am, mtcars)
summary(fit_mtcars)
```

I can confirm mean mpg of automatic transmission is 17.147, and mean mpg of manual transmission is 7.245 more. 

```{r linear plot}
par(mfrow=c(1,2))

# plot the linear graph
mtcars_fitted<-fitted(fit_mtcars)

plot(mtcars$mpg,main="MPG Real & Fitted value",xlab="",ylab="MPG",ylim=c(10,34),col=c("blue","red")[mtcars$am])
par(new=T)
plot(mtcars_fitted,type="l",xlab="",ylab="",ylim=c(10,34),col="green",lwd=2)

plot(residuals(fit_mtcars),main="Residuals",Xlab="",ylab="Residuals")
abline(h=0,col="red")
```

The blue point is the mpg value of automatic transmission, and the red point is the mpg value of manual transmission. The green line is fitted line, and it means the predicted value using linear regression.
The right graph is residuals of linear regression model. 

### Multiple linear regression

In order to model selection, I am going to use backward elimination method, which removes variables sequentially. First, I starts with the model that includes all variables. Next, I exclude a variable in order, as comparing with adjusted R squared value.

```{r multiple linear regression}
# Check the overall parameters
fit_overall<-lm(mpg~.,mtcars)
summary(fit_overall)

plot(mtcars)

# Exclude the variables sequentially, and compare the R squared value
fit_ex_cyl<-lm(mpg~disp+hp+drat+wt+qsec+vs+am+gear+carb,mtcars)
summary(fit_ex_cyl)
fit_ex_vs<-lm(mpg~disp+hp+drat+wt+qsec+am+gear+carb,mtcars)
summary(fit_ex_vs)
fit_ex_carb<-lm(mpg~disp+hp+drat+wt+qsec+am+gear,mtcars)
summary(fit_ex_carb)
fit_ex_gear<-lm(mpg~disp+hp+drat+wt+qsec+am,mtcars)
summary(fit_ex_gear)
fit_ex_drat<-lm(mpg~disp+hp+wt+qsec+am,mtcars)
summary(fit_ex_drat)

fit_ex_disp<-lm(mpg~hp+wt+qsec+am,mtcars)
summary(fit_ex_disp)
fit_ex_hp<-lm(mpg~wt+qsec+am,mtcars)
summary(fit_ex_hp)
```

When I use all varibles, the adjusted R squared value is 0.8066. As I exclude variables, "cyl", "vs", "carb", "gear", "drat", the adjusted R squared value goes up to 0.8375. However, when I exclude more variables, the adjusted R squared value goes down. So if "disp", "hp", "wt", "qsec", "am" are used, regression model is the best.

```{r multivariate linear regression}
# Use anova function
anova(fit_mtcars,fit_ex_drat)

# plot
par(mfrow=c(2,2))
plot(fit_mtcars)

par(mfrow=c(2,2))
plot(fit_ex_drat)
```

P-value is less than 0.05, so I reject the null hypothesis and claim that multivariate model is different from simple linear regression model. 

## Result
In conclusion, manual transmission cars are better mpg than automatic transmission cars. The average mpg is 7.24 higher, and there is relationship between mpg and transmission ways. Besides, if we consider additional variables, such as "disp", "hp" and so on, we can make more sophisticated regression model. 
